Causal Impact of Masks, Policies, Behavior on Early Covid-19 Pandemic in the U.S.

### 2020-09-07 tex/covidEffectOfNPI-revision.tex
update

Given the lack of experimental evidence on the effect of masks in the context of COVID-19, conducting observational studies  is useful and important. To the best of our knowledge, our paper is the first  empirical study that shows the effectiveness of  mask mandates on reducing the spread of Covid-19 by analyzing the US state-level data. This finding corroborates and is complementary to the medical observational evidence in \cite{howard2020}. Analyzing mitigation measures in New York, Wuhan, and Italy, \cite{zhangr2020} conclude that mandatory face coverings substantially reduced infections. \cite{abaluck2020}  find that the growth rates of cases and of deaths in countries with pre-existing norms that sick people should wear masks are lower by 8 to 10\% than those rates in countries with no pre-existing mask norms.\footnote{\cite{miyazawa2020} find that  country's COVID-19 death rates are negatively associated with mask wearing rates.} The Institute for Health Metrics and Evaluation at the University of Washington  assesses that, if 95\% of the people in the US were to start wearing masks from early August of 2020, 66,000 lives would be saved by December 2020 \citep{IHME2020}.
Our finding is also independently corroborated by a completely different causal methodology based on synthetic control
using German data in \cite{Mitze2020}.\footnote{Our study was first released in ArXiv on May 28, 2020 whereas
 \cite{Mitze2020} was released at SSRN on June 8, 2020. }

>>>>

Given the lack of experimental evidence on the effect of masks in the context of COVID-19, conducting observational studies  is useful and important. To the best of our knowledge, our paper is the first  empirical study that shows the effectiveness of  mask mandates on reducing the spread of Covid-19 by analyzing the US state-level data. This finding corroborates and is complementary to the medical observational evidence in \cite{howard2020}. Analyzing mitigation measures in New York, Wuhan, and Italy, \cite{zhangr2020} conclude that mandatory face coverings substantially reduced infections. \cite{abaluck2020}  find that the growth rates of cases and of deaths in countries with pre-existing norms that sick people should wear masks are lower by 8 to 10\% than those rates in countries with no pre-existing mask norms.\footnote{\cite{miyazawa2020} find that  country's COVID-19 death rates are negatively associated with mask wearing rates.} The Institute for Health Metrics and Evaluation at the University of Washington  assesses that, if 95\% of the people in the US were to start wearing masks from early August of 2020, 66,000 lives would be saved by December 2020 \citep{IHME2020}, which is largely consistent with our results.
Our finding is also independently corroborated by a completely different causal methodology based on synthetic control
using German data in \cite{Mitze2020}.\footnote{Our study was first released in ArXiv on May 28, 2020 whereas
 \cite{Mitze2020} was released at SSRN on June 8, 2020. }
